Publicity Outreach for ``Quantum interval-valued probability: Contextuality and the Born rule''

### 2018-04-12 revised_prop_letter_publicity.tex
revised_prop_letter_publicity.lyx Updating...

\maketitle
Randomness is used in cryptography, randomized algorithms, and gambling...
etc. However, it is impossible to test randomness directly~\cite{Shi2015}.
While some people believed quantumness implies randomness, to prove
randomness of quantum theory is to prove that quantum theory cannot
be simulated by any deterministic hidden variable theory. Although
the Bell \cite{Bell1964,Redhead1987-REDINA,peres1995quantum,Jaeger2007}
and Kochen-Specker \cite{BELL_1966,kochenspecker1967,Redhead1987-REDINA,Mermin1990Simple,peres1995quantum,Jaeger2007,Held2016}
theorems exclude non-local and non-contextuality deterministic hidden
variable theories.

>>>>

\maketitle
Randomness is used in cryptography, randomized algorithms, and gambling...
etc. However, it is impossible to test randomness directly~\cite{Shi2015}.
While some people believed quantumness implies randomness~\cite{Shi2015,Yuan2017},
the randomness of quantum theory cannot be established if we can simulate
quantum theory by a deterministic hidden variable theory. Although
the Bell \cite{Bell1964,Redhead1987-REDINA,peres1995quantum,Jaeger2007}
and Kochen-Specker \cite{BELL_1966,kochenspecker1967,Redhead1987-REDINA,Mermin1990Simple,peres1995quantum,Jaeger2007,Held2016}
theorems exclude any non-local and non-contextuality deterministic
hidden variable theory. However, any physical measurement can only
be done with finite precision, and Meyer~\cite{PhysRevLett.83.3751}
claimed that finite-precision measurements invalidate the spirit of
the Kochen-Specker theorem. In this investigation~\cite{THOS2018},
we employ an interval-valued framework to establish bounds on the
validity of the Kochen-Specker theorem in realistic experimental environments.
In another word, when physical measurements are precise enough, the
Kochen-Specker theorem remains valid, i.e., quantum theory should
not be simulated a non-contextuality deterministic hidden variable
theory. Hence, our results provide additional trust of the randomness
of quantum theory.
